### 2018-06-12 ident/docs/sifigures.tex
significant changes to methods and results and change in order of sections and figures in SI

\externaldocument{draft_3} % reference to existing external document

\captionsetup{font={stretch=2.0}}
\begin{document}
	\begin{center}
		\begin{Large}
			Manuscript Title 
		\end{Large}\\
		Shyam Srinivasan\textsuperscript{a}, William R. Cluett\textsuperscript{a} and Radhakrishnan Mahadevan\textsuperscript{*,a,b}\\
	\end{center}	
\section{Supplementary Tables}
\begin{table}[!thbp]
	\caption{Table showing the perturbed values of all parameters used to generate experimental data in silico for testing practical identifiability of all fluxes in the small metabolic network.}
	\begin{center}				
		\begin{tabular}{lp{3.5cm}cccccp{2cm}}
			\hline
			Experiment Type & Perturbed Parameter (wild type value a.u.)& \multicolumn{5}{c}{Perturbed Values a.u.} & Number of Experiments\\
			\hline
			wild type &  &\multicolumn{5}{l}{} & 1\\
			acetate perturbation & $acetate$ (0.1) & 0.05 & 0.09 & 0.2 & 0.5 & 1.0 & 5\\
			$v_1$ perturbation & $k_1^{cat}$ (1) & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 & 5\\				
			$v_2$ perturbation & $V_2^{max}$ (1) & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 & 5\\								
			$v_3$ perturbation & $V_3^{max}$ (1) & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 & 5\\
			\hline
			\multicolumn{7}{l}{Total number of experimental data sets used for practical parameter identification:} & 21\\
			\hline
		\end{tabular}
	\end{center}	
	\label{tab:pval}
\end{table}

@@

\section{Supplementary Figures}	
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v1_kcat_ck_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$ when there is no noise in the input experimental data. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v1_kcat_ck_values}
\end{figure}

@@

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=1.0\textheight, keepaspectratio]{figures/parameter_dist/v1_vmax_ck_parameter_values}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$, which is described using as a Michaelis-Menten model, without using the enzyme concentration $E$ for identification when there is no noise in the input experimental data. Here $V_1^{max} = k_1^{cat}E$. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v5_v1max_ck_values}
\end{figure}

@@

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=0.6\textwidth,height=0.6\textheight,keepaspectratio]{figures/figure3/experimental_design}}
	\caption{Flow diagram showing a method for experimental design that uses our methodology for practical identification of parameters to determine the number and type of experiments required to identify all fluxes within a given metabolic network.}\label{fig:ident-design}
\end{figure}

>>>>

\externaldocument{draft_4} % reference to existing external document

\captionsetup{font={stretch=2.0}}
\begin{document}
	\begin{center}
		\begin{Large}
			Manuscript Title 
		\end{Large}\\
		Shyam Srinivasan\textsuperscript{a}, William R. Cluett\textsuperscript{a} and Radhakrishnan Mahadevan\textsuperscript{*,a,b}\\
	\end{center}

\begin{table}[!thbp]
	\caption{Table showing the perturbed values of all parameters used to generate experimental data in silico for testing practical identifiability of all fluxes in the small metabolic network.}
	\begin{center}				
		\begin{tabular}{lp{3.5cm}cccccp{2cm}}
			\hline
			Experiment Type & Perturbed Parameter (wild type value a.u.)& \multicolumn{5}{c}{Perturbed Values a.u.} & Number of Experiments\\
			\hline
			wild type &  &\multicolumn{5}{l}{} & 1\\
			acetate perturbation & $acetate$ (0.1) & 0.05 & 0.09 & 0.2 & 0.5 & 1.0 & 5\\
			$v_1$ perturbation & $k_1^{cat}$ (1) & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 & 5\\				
			$v_2$ perturbation & $V_2^{max}$ (1) & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 & 5\\								
			$v_3$ perturbation & $V_3^{max}$ (1) & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 & 5\\
			\hline
			\multicolumn{7}{l}{Total number of experimental data sets used for practical parameter identification:} & 21\\
			\hline
		\end{tabular}
	\end{center}	
	\label{tab:pval}
\end{table}

@@

\section{Supplementary Figures}	
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=0.6\textwidth,height=0.6\textheight,keepaspectratio]{figures/figure3/experimental_design}}
	\caption{Flow diagram showing a method for experimental design that uses our methodology for practical identification of parameters to determine the number and type of experiments required to identify all fluxes within a given metabolic network.}\label{fig:ident-design}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=1.0\textheight, keepaspectratio]{figures/parameter_dist/v1_vmax_ck_parameter_values}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$, which is described using as a Michaelis-Menten model, without using the enzyme concentration $E$ for identification when there is no noise in the input experimental data. Here $V_1^{max} = k_1^{cat}E$. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v1_v1max_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v1_kcat_ck_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$ when there is no noise in the input experimental data. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v1_kcat_ck_values}
\end{figure}

@@

@@
